Visualizing Project Evolution Through Abstract Syntax Tree Analysis

### 2016-06-27 paper/document.tex
Add reference to RQs.
Remove reference of screencast.

Although rich in detail, the AST diffs are difficult to analyze if displayed in their raw form; hence, we created an HTML5 web visualization application which is intended for developers, project managers, and researchers to use (Figure~\ref{fig:main-view}). The source code for TypeV---both the AST differencing component and the web application---is available online on GitHub.\footnote{\url{https://github.com/mdfeist/TypeV}} A screencast demonstrating its use is also available online.\footnote{\url{https://archive.org/details/typev-demo}}

@@

In the following sections, we present case studies demonstrating the extra insight that the AST differencing provides.

>>>>

Although rich in detail, the AST diffs are difficult to analyze if displayed in their raw form; hence, we created an HTML5 web visualization application which is intended for developers, project managers, and researchers to use (Figure~\ref{fig:main-view}). The source code for TypeV---both the AST differencing component and the web application---is available online on GitHub.\footnote{\url{https://github.com/mdfeist/TypeV}}

@@

\textbf{RQ3}: What extra insight can we gain from type-based visualization? We present case studies demonstrating the insight AST differencing can provide.
